---
output: rmarkdown::github_document
---

wayback : Tools to Work with the Various Internet Archive Wayback Machine APIs

[![Travis-CI Build Status](https://travis-ci.org/jonocarroll/wayback.svg?branch=master)](https://travis-ci.org/jonocarroll/wayback)
[![Coverage Status](https://img.shields.io/codecov/c/github/jonocarroll/wayback/master.svg)](https://codecov.io/github/jonocarroll/wayback?branch=master)

The following functions are implemented:

- `archive_available`:	Does the Internet Archive have a URL cached?
- `cdx_basic_query`:	Perform a basic/limited Internet Archive CDX resource query for a URL
- `get_mementos`:	Retrieve site mementos
- `get_timemap`:	Retrieve a timemap for a URL

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/wayback")
```

```{r message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(wayback)
library(tidyverse)

# current verison
packageVersion("wayback")

archive_available("https://rud.is/b")

get_mementos("https://rud.is/b")

get_timemap("https://rud.is/b")

cdx_basic_query("https://rud.is/b") %>% 
  glimpse()
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(wayback)
library(testthat)

date()

test_dir("tests/")
```
