---
output: rmarkdown::github_document
---

`wayback` : Tools to Work with Internet Archive Wayback Machine APIs

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/wayback.svg?branch=master)](https://travis-ci.org/hrbrmstr/wayback)
[![codecov](https://codecov.io/gh/hrbrmstr/wayback/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/wayback)
[![Appveyor Status](https://ci.appveyor.com/api/projects/status/w9rwdf8a16t0amht/branch/master?svg=true)](https://ci.appveyor.com/project/hrbrmstr/wayback/branch/master)

The following functions are implemented:

- `archive_available`:	Does the Internet Archive have a URL cached?
- `cdx_basic_query`:	Perform a basic/limited Internet Archive CDX resource query for a URL
- `get_mementos`: Retrieve site mementos from the Internet Archive
- `get_timemap`:	Retrieve a timemap for a URL
- `read_memento`:	Read a resource directly from the Time Travel MementoWeb
- `is_memento`: Various memento-type testers (useful in `purrr` or `dplyr` contexts)
- `is_first_memento`: Various memento-type testers (useful in `purrr` or `dplyr` contexts)
- `is_next_memento`: Various memento-type testers (useful in `purrr` or `dplyr` contexts)
- `is_prev_memento`: Various memento-type testers (useful in `purrr` or `dplyr` contexts)
- `is_last_memento`: Various memento-type testers (useful in `purrr` or `dplyr` contexts)
- `is_original`: Various memento-type testers (useful in `purrr` or `dplyr` contexts)
- `is_timemap`: Various memento-type testers (useful in `purrr` or `dplyr` contexts)
- `is_timegate`: Various memento-type testers (useful in `purrr` or `dplyr` contexts)

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/wayback")
```

```{r message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(wayback)
library(tidyverse)

# current verison
packageVersion("wayback")
```


```{r avail, message=FALSE, warning=FALSE, error=FALSE}
archive_available("https://yahoo.com/")
```

```{r get_memento, message=FALSE, warning=FALSE, error=FALSE}
get_mementos("https://yahoo.com/")
```

This one takes too long to regen every time
```{r get_time, message=FALSE, warning=FALSE, error=FALSE, eval=FALSE}
get_timemap("https://yahoo.com/")
```

```{r basic_q, message=FALSE, warning=FALSE, error=FALSE}
cdx_basic_query("https://yahoo.com/", limit = 10) %>% 
  glimpse()
```

```{r read_mem, message=FALSE, warning=FALSE, error=FALSE}
res <- read_memento("https://yahoo.com/")
res <- stringi::stri_split_lines(res)[[1]]
res <- c(head(res, 6), tail(res, 8))
cat(paste0(res, collaspe="\n"))
```
